\Chapter{Summary}

In my thesis i compared the most popular JavaScript frameworks. In the first part i demonstrated that what is the MVC framework, what is the difference between JavaScript and ECMAScript, there was a part of the versions and lastly a historical overview. Thereafter an overview of JavaScript technologies.\\
The main subject was to compare the frameworks and libraries in a few aspects. Those are the CRUD operations, templates, routing, filters, directives, form validation, and also login with an option to sign up.
The four web applications what i implemented are AngularJS, Angular 2, Vue.js, and React.js. The MongoDB database and the Node.js server provides the backend functionalities. These web applications are deal with MMA Fighters. There is an option to log in or sign up, to add a new fighter, to see the fighters who are stored in the database, to filter the table of fighters, to edit the fighter's details and to delete the fighters.\\ The AngularJS framework is a very good option to develop web applications, and it is not really hard to learn for those who are not proficient in the web pages world. Maintaining and testing the separated parts is really easy to handle. The two-way data binding is simplify the development phase. In Angular 2, React.js, and Vue.js the option to generate the components and services with their CLI-s is very handy. These frameworks are well-known and very popular in firms. The Vue.js is a framework which is combine the advantages of the other frameworks. It is a fast alternative, and growing quickly. 
Because of the JSX and ES6 elements the React.js is need more time and efforts to learn how to use the library.\\
The Auth0 platform is a powerful and popular solution to integrate into any web application. It has a well-founded documentation, and support the most popular frameworks and API-s.\\
My further plans and ideas to work on in these applications are to add new functions, like image uploading for the fighter's image field, create a custom login and signup form with Auth0, and also to create an administrator and guest interface.\\
Each one of these frameworks has advantages over the others, and also has disadvantages as well, which the developers or firms could accept.
In my opinion it is a good opportunity to choose from this big lineup of technologies and take time to meet and learn them. 




