\Chapter{Summary}

In my thesis I have compared the most popular JavaScript frameworks. In the first part, I demonstrated the concept of MVC frameworks, the relation of JavaScript and ECMAScript, which contains a historical overview with version numbers. After, I have mentioned the different types of JavaScript technologoies.

The main subject of this work is to compare the main aspects of the JavaScript MVC frameworks. These aspects are the CRUD operations, templating, routing, application of filters and directives, form validation, and also the authentication.

I have implemented sample web applications in AngularJS, Angular 2, Vue.js, and React. The MongoDB database and the Node.js server provides the backend functionalities. These web applications deal with MMA Fighters. There is an option to log in or sign up, to add a new fighter, to see the fighters who are stored in the database, to filter the table of fighters, to edit the details of fighter profile and to delete the fighters.

The AngularJS framework is a very good option to develop web applications, and it is not really hard to learn for those who are not proficient in the web development. Maintaining and testing the separated parts is really easy to handle. The two-way data binding is simplify the development phase. 

In Angular 2, React.js, and Vue.js the option to generate the components and services with their CLI-s is very handy. These frameworks are well-known and very popular in the industry. The Vue.js is a framework which combines the advantages of the other frameworks. It is a very efficient alternative, and its popularity growing quickly.

Because of the JSX and ES6 elements the React, it requires more time and efforts to learn how to use the library.

The Auth0 platform is a powerful and popular solution for implementing authentication in any type of web applications. It has a well-founded documentation, and support the most popular frameworks and API-s.

My further plans are to add new functions to the sample applications, like image uploading for the fighter's image field, create a custom login and signup form with Auth0, and also to create an administrator and guest interface.

Each one of these frameworks have advantages over the others, and also have disadvantages as well, which can be acceptable or rejectable for the developers and for the firms. In my opinion, it is a good opportunity to choose from this big lineup of technologies and take time to meet and learn them. 
